---
title: "Auction Modeling"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(
        echo = TRUE
)
knitr::opts_knit$set(
        stop_on_error = 2L
)
knitr::opts_chunk$set(
        fig.path = "man/figures/"
)
```


# auctionr

## Overview 

A package for R to estimate private-value auction models while allowing for unobservable auction-specific heterogeneity.

## Installation

```{r, eval = FALSE}
# Install a necessary dependency
install.packages("numDeriv")

# Download a ZIP archive of the repo from https://code.harvard.edu/HBS/rcs_amackay__auctionr
# Install the package
install.packages("[local path to the archive]", repos = NULL, type = "source")
```


## Getting started

There are two functions available in the package:

* `auction_generate_data()` allows the user to generate sample data from the principal model used in the package. 

* `auction_model()` calculates maximum likelihood estimates of parameters of the principal model for the data provided by the user.

```{r}
library(auctionr)

set.seed(100)
dat <- auction_generate_data(obs = 100, mu = 10, alpha = 2, sigma = 0.2,
                             beta = c(-1,1), new_x_mean= c(-1,1), new_x_sd = c(0.5,0.8))

res <- auction_model(dat,
                    init_param =  c(8, 2, .5, .4, .6),
                    num_cores = 1,
                    method = "BFGS",
                    control = list(trace=1, parscale = c(1,0.1,0.1,1,1)),
                    std_err = TRUE)
```

## For further information

## License

