---
title: "Auction Modeling"
output: md_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
        echo = TRUE
)
knitr::opts_knit$set(
        stop_on_error = 2L
)
knitr::opts_chunk$set(
        fig.path = "man/figures/"
)
```

## Auction Modeling

Package for R to estimate private-value auction models while allowing for unobservable
auction-specific heterogeneity. Extensions to the baseline model allow for endogenous 
entry and observing multiple bids per auction.

## Motivation 

This is a test.

## Examples

The `beta_plot` function allows you to simulate data from a 
beta distribution and plot the results.

```{r}
library(auctionmodeling)
#MYFUNCTIONGOESHERE(withparams = TRUE)
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
