---
title: "Auction Modeling"
output: md_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
        echo = TRUE
)
knitr::opts_knit$set(
        stop_on_error = 2L
)
knitr::opts_chunk$set(
        fig.path = "man/figures/"
)
```

# auctionmodeling

## Overview 

An R package for R to estimate private-value auction models while allowing for unobservable
auction-specific heterogeneity. Extensions to the baseline model allow for endogenous 
entry and observing multiple bids per auction.


## Installation

```{r, eval = FALSE}
# Install the R package from CRAN:
install.packages("auctionmodeling")

# Or the the development version from GitHub:
# install.packages("devtools")
devtools::install_github("alexjmac/auctionmodeling")
```


## Getting started

```{r}
library(auctionmodeling)
#MYFUNCTIONGOESHERE(withparams = TRUE)
```

There are two functions availabe from the package:

* `auction_generate_data()` which xxxx

* `model_auction()` which does the real work. Here, ...

## For further information

xxx

## License

